\section{AEON Community}

\subsection{Links}
\subsubsection{Social/Community}
\begin{tabbing}
Website:~~~~~~~~~~~~~~~~~~ \= https://www.aeon.cash/ \\
BitcoinTalk ANN: \> https://bitcointalk.org/index.php?topic=641696.0\\
Discord invite:	\> https://discord.gg/TM8mEsx \\
Github: \> https://github.com/aeonix		(source, binaries, wallets)\\
IRC: \> https://webchat.freenode.net 		(channel:  \#aeon)\\
Medium blog: \> https://medium.com/@AEON\_Community \\
Reddit: \> https://www.reddit.com/r/Aeon/\\
Telegram: \> https://telegram.me/AEONgroup\\
Twitter: \> https://twitter.com/AeonCoin
\end{tabbing}

\subsubsection{Block Explorers}
\begin{tabbing}
AeonBlocks:~~~~~~~~~~~~~ \= https://aeonblocks.com/ \\
Onion Aeon: \> http://aeon.lol/ or http://162.210.173.150/ \\
Onion Aeon Testnet: \> http://testnet.aeon.lol/ or http://162.210.173.151/ \\
Onion Aeon Stagenet: \> http://162.210.173.151:8083/ \\
AEON Charts: \> https://stoffu.github.io/diff-chart/
\end{tabbing}

\subsection{Mining}
\subsubsection{Mining Applications}
The most popular mining applications are \textbf{xmr-stak} and \textbf{xmrig}.  For additional options, check with the community.

\subsubsection{Mining Pools}
There are several AEON mining pools operating. It is recommended to join a small to medium sized pool, to spread out the hashes across the network as much as possible.  Look on the community sites to find links to current AEON mining pools.

\subsection{Exchanges}
Visit the AEON website to find a current list of exchanges which trade AEON.

\subsection{Wallets}
\textbf{aeon-wallet-cli} is the default command-line wallet that comes with the AEON node daemon.\\
\\
\textbf{Aeon Monerujo} is a light mobile wallet for Android which connects to a remote node of your choosing, and supports QR Code scanning.\\
\\
\textbf{Aeon Daemon} is a full node that runs on Android, and is available in the Google Play Store. It requires synchronizing the entire block chain to the device.

\subsection{Development Team}
Lead developer:		smooth\\
Contributing developer:	stoffu

\subsection{Current Work and Future Plans}
\subsubsection{Work In 2018}
\textbf{Core Development:}
\begin{itemize}
	\item Implement RingCT logic. This is an improvement to ring signatures which also obscures the \textit{amount} of a transaction on the blockchain.
	\item Implement the Bulletproofs improvement to RingCT. This will drastically reduce transaction sizes, making the blockchain more scalable.
\end{itemize}
\textbf{Community Work:}
\begin{itemize}
	\item New Community Project Funding System
	\item AEONStats -- extended network and usage stats for the blockchain
	\item Pay with AEON -- payment gateways for popular eCommerce systems
	\item AEON gambling site
	\item AEON API -- pay Bitcoin with AEON
	\item Various AEON How-To's
\end{itemize}

\subsubsection{Future Plans}
\begin{itemize}
	\item Greater selection of wallets, including mobile and cold storage
	\item Community-funded marketing
\end{itemize}

