\section{AEON Features}
AEON stands for Anonymous Electronic ON-line Coin, and it was launched on June 6, 2014 at 6:00 PM UTC. The following features are critical to our vision of a digital currency for everyone.

\subsection{Secure}
AEON takes security seriously.  Each transaction is secured with robust cryptography and distributed through a global peer-to-peer consensus network.  The cryptographic implementation ensures that nobody is able to “steal” an online transaction, and a coin’s owner is unable to spend the coin more than once.

\subsection{Lightweight}
AEON seeks to be \textbf{mobile-friendly} by implementing, among other things, the following technical features:
\begin{itemize}
	\item A lightweight Proof-of-Work algorithm
	\item Blockchain pruning
	\item Optional lightweight traceable transactions
\end{itemize}
With this intentional focus, AEON requires a smaller technology footprint, and the time to sync with the blockchain on lower end devices improves by a factor of 10. 

\subsection{Private and Untraceable}
Privacy is paramount. Funds are transferred without the identifying information of the user becoming visible on the blockchain. In addition, the receiving wallet addresses are obfuscated with ring signature technology and non-repeating one-time addresses derived from the receiving public key. These measures make the blockchain highly resistant to analysis.

\subsection{Low Barrier to Participation}
Founded as an Open Source project, AEON is free to use without restriction, and 100\% of funding is by voluntary community donations; there is no Development Tax imposed on miners.  In addition, there was no premine or instamine (a practice by which the developers gain a large percentage of the coins before allowing other miners to be involved). The network is resistant to specialized hardware, allowing more people to participate directly with their PC by mining or running a full node.  Everyone is welcome to contribute to the ongoing effort, financially or otherwise.\\
\\
NOTE:  Many of the points referenced above will be covered in more detail in section \ref{secImp} \textit{AEON Implementation}.