
\section{Vision}
	
	\textbf{AEON isn't just a currency.  \textit{It's a lifestyle}.}\\
	\\
	Technology impacts our financial lives in new ways every day, and the pace of change is accelerating. Only in the last 15 years has broadband internet become widely available, giving rise to the concept of online marketing and commerce. In the last 5 years, mobile phones have advanced to rival desktop usage for online purchases.  Researchers are now estimating that by 2021 there may be over 2 billion mobile banking users.\\
	\\
	\textbf{Truly, we are realizing a more convenient reality with our personal finances.}\\
	\\
	This convenience, however, comes with many challenges. On any given day, it is not difficult to find a news story about financial accounts being hacked and/or personal identity information being stolen.  And in spite of the technological advances, the current ecommerce solutions cannot solve the problems inherent with local currencies; such as the difficulty of transacting across national borders, and the occasions when centralized powers negatively impact economies via poor decisions or manipulation.\\
	\\
	\textbf{Enter the concept of decentralized digital currency.}\\
	\\
	Imagine a lifestyle where personal financial management is not only convenient and mobile, but also secure, private, and impervious to national borders and centralized control.\\
	\\
	AEON is about enabling this era, enabling an age where all people everywhere have the freedom to privately send and receive money with whatever gadget they already own.\\
	\\
	\textbf{\textit{This lifestyle is closer than you think...}}\\
	
